Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-07-22 Papers/ms.tex
Another paragraph

>>>>

{\tt Upper limits on mass}

As with any inference, the results presented here may be sensitive to many of
the input modelling assumptions, and a slightly different (yet still
``reasonable'') set of choices might yield different results. For example, if
the density profile of the lens was smooth but not of the SIE form, and the
data were informative enough to show this, the current
model would only be able to explain the data by adding substructures. Hence, an alternative explanation for these results is that, rather than containing a substructure, the density profile of the lens is simply not within
the SIE family. One way of investigating this is to use a different family of
smooth lens models and doing model selection based on the marginal likelihoods.
